### 2011-08-13 doc/theses/vitasek/diplomka.tex
Thesis: in progress

\begin{figure}
  \caption{Realistic data - first part}
  \label{image-experiments-data-realistic-1}
  \centering
    \subfigure[OVA1]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA1.eps}}
    \subfigure[OVA2]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA2.eps}}
    \subfigure[OVA3]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA3.eps}}
\end{figure}

\begin{figure}
  \caption{Realistic data - second part}
  \label{image-experiments-data-realistic-2}
  \centering
    \subfigure[XMA-c]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMA-c.eps}}
    \subfigure[XMA-p]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMA-p.eps}}
    \subfigure[XMD]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMD.eps}}
\end{figure}

@@

\begin{figure}
  \caption{Realistic data with converted attributes}
  \label{image-experiments-data-converted}
  \centering
    \subfigure[MSH]{\includegraphics[width=0.45\textwidth]{images/experiments/data/converted/MSH.eps}}
    \subfigure[NTH]{\includegraphics[width=0.45\textwidth]{images/experiments/data/converted/NTH.eps}}
\end{figure}

@@

TODO talk about some "density".

@@

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
%  	\subfigure[100-100]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-100.eps}}
%	\subfigure[100-200]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-200.eps}}
%    \subfigure[100-1000]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/100-1000.eps}}    
\end{figure}

>>>>

\begin{table}
  \caption{List of realistic test data files}
  \label{table-experiments-data-realistic}
  \centering
  \begin{tabular}{l | r | c | c | l}
	Name  & Size [kb] & Vertices & Edges & Optimum \\
	\hline
	OVA1  & 4.5 & 29 & 43 & 0.45588235294117635 \\
	OVA2  & 11.9 & 23 & 36 & 0.1634615384615385  \\ 
	OVA3  & 237.6 & 31 & 47 & 0.25537156151635415 \\
	XMA-c & 1 807.7 & 1  & 0  & 0.7546666666666667  \\
	XMA-p & 13 748.3 & 1  & 0  & 0.2019306150568969  \\
	XMD   & 1 743.0 & 17 & 15 & 0.09786094165493507 \\
  \end{tabular}
\end{table}

TODO explain edges, vertices and say that opt is the known for alpha = beta = 1

\begin{figure}
  \caption{Realistic data}
  \label{image-experiments-data-realistic}
  \centering
    \subfigure[OVA1]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA1.eps}}
    \subfigure[OVA2]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA2.eps}}
    \subfigure[OVA3]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/OVA3.eps}}
    \subfigure[XMA-c]{\includegraphics[width=0.08\textwidth]{images/experiments/data/realistic/XMA-c.eps}}
    \subfigure[XMA-p]{\includegraphics[width=0.08\textwidth]{images/experiments/data/realistic/XMA-p.eps}}
    \subfigure[XMD]{\includegraphics[width=0.45\textwidth]{images/experiments/data/realistic/XMD.eps}}
\end{figure}

@@

\begin{table}
  \caption{List of realistic test data files with converted attributes}
  \label{table-experiments-data-converted}
  \centering
  \begin{tabular}{l | r | c | c | l}
	Name  & Size [kb] & Vertices & Edges & Optimum \\
	\hline
	MSH  & 3 100.5 & 1 & 0 & 0.5416472778036296 \\
	NTH  & 2 523.5 & 5 & 7 & 0.057918595422124436 \\ 
  \end{tabular}
\end{table}

\begin{figure}
  \caption{Realistic data with converted attributes}
  \label{image-experiments-data-converted}
  \centering
    \subfigure[MSH]{\includegraphics[width=0.08\textwidth]{images/experiments/data/converted/MSH.eps}}
    \subfigure[NTH]{\includegraphics[width=0.45\textwidth]{images/experiments/data/converted/NTH.eps}}
\end{figure}

@@

TODO talk about some "density". Explain what is the max number of edges

@@

\begin{table}
  \caption{List of artificial test data files}
  \label{table-experiments-data-artificial}
  \centering
  \begin{tabular}{l | r | c | c | c | c | l}
	Name  & Size [kb] & Vertices & Edges & $|E| / |V|$ & $|E| / |E_{max}|$ & Optimum \\
	\hline
	100-100  & 8.4  & 99 & 95  & 0.95 & 0.02 & 0.836666666666667 \\
	100-200  & 13.0 & 96 & 174 & 1.81 & 0.04 & 0.726000000000000 \\ 
    100-1000 & 49.5 & 93 & 754 & 8.11 & 0.16 & 0.380952380952381 \\ 
  \end{tabular}
\end{table}

\begin{table}
  \caption{List of ``sized" artificial test data files}
  \label{table-experiments-data-artificial-size}
  \centering
  \begin{tabular}{l | r | c | c | c | c | l}
	Name  & Size [kb] & Vertices & Edges & $|E| / |V|$ & $|E| / |E_{max}|$ & Optimum \\
	\hline
	0-0     & 0.2  & 0  & 0   & -    & -    & 0.0                \\
	10-5    & 0.6  & 10 & 5   & 0.50 & 0.11 & 0.8500000000000002 \\ 
    20-20   & 1.7  & 18 & 13  & 0.72 & 0.08 & 0.7166666666666669 \\
   	30-45   & 3.1  & 29 & 43  & 1.48 & 0.11 & 0.7083333333333334 \\ 
	40-80   & 5.1  & 39 & 72  & 1.85 & 0.10 & 0.6950000000000002 \\
	50-125  & 7.5  & 48 & 111 & 2.31 & 0.10 & 0.6566666666666666 \\
	60-180  & 10.4 & 58 & 157 & 2.71 & 0.09 & 0.6214285714285716 \\
	70-245  & 13.8 & 67 & 205 & 3.06 & 0.09 & 0.5982142857142856 \\
	80-320  & 17.6 & 76 & 261 & 3.43 & 0.09 & 0.5791666666666667 \\
	90-405  & 21.9 & 86 & 352 & 4.09 & 0.10 & 0.528888888888889  \\
	100-500 & 26.7 & 91 & 388 & 4.26 & 0.09 & 0.4981818181818182 \\
  \end{tabular}
\end{table}

TODO explain why the optimum is getting smaller

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
    % TODO fix cropping
  	\subfigure[48-80]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/size/40-80.eps}}
	\subfigure[70-245]{\includegraphics[width=0.45\textwidth]{images/experiments/data/artificial/size/70-245-fixed.eps}}
\end{figure}

TODO why we have less than declared number? because of how we created it
